A simulation model of DNA methylation data

### 2015-04-06 Rmarkdown/methsim.Rmd
Various methsim TODOs and rejigging

@@

In `methsim`, the routine to simulate $\{ \mathbf{{Z_{\tilde{h}}}} \}_{\tilde{h} = 1}^{n_{\tilde{h}}}$ is available as the `simulate,SimulateMethylomeParam-method`. It is mostly written in C++ using the wonderful Rcpp package \citep{Eddelbuettel:2011to, Eddelbuettel:2013if}, which greatly speeds up the running time.

@@

-  __TODO: Figure showing 'rest of genome' is MMRs. More generally, a figure showing the average methylation level in each of `UMR`, `LMR`, `PMR` and `other`.
- [ ] DONE

@@

>>>>

__TODO: Figure showing `other` is MMRs. More generally, a figure showing the average methylation level in each of `UMR`, `LMR`, `PMR` and `other`.__

@@

@@

@@

__TODO: Work the comparison to other methods into my conclusions__
